Social Visual Analytics: DevOps for Data Scientists

### 2015-02-19 discussion.tex
Yes

Returning to Heer and Agrawala's design considerations, our experience
underscores the relevance of their proposals, and indicates areas
for further exploration. We briefly examine these aspects of the
visual analytics environment.

{\bf Shared artifacts and artifact histories} are a central feature
of RCloud. The prototype aimed at making it convenient to collaborate
on experimental workbooks and the resulting analyses. We observed
that hackers readily shared ideas through RCloud. They used RCloud
to discuss data analysis, programming problems, and to publish results
by sharing URLs instead of instead of embedding screenshots in
PowerPoint. Artifact histories are provided through git. It is fair
to criticize that it is not human-friendly, but we assume RCloud
hackers are already familiar with it.

{\bf Modularity and granularity.} The ability to segment work into
independent units (modularity) is a key to working in teams. It is
further an advantage if the units may be kept small, and team members
can realize benefits that are at least proportional to their work
on these units (granularity). RCloud's notebook and versioning
capabilities allow work to be divided into units as fine as
the underlying language allows, and versioning encourages making
incremental changes at low cost and without disrupting the work
of others.

{\bf View sharing, bookmarking.} Most resources in RCloud are named
and accessed as URLs. This proved to be an effective mechanism for
sharing, and for analyses to be integrated with external processes
and systems.

{\bf Discussion.} Annotation and commenting was another central goal.
Commenting is supported through github, but our hackers found it
awkward and did not exercise it as much as we expected.
making it a bit awkward and
not as widely used as we hoped.  More elaborate annotation was not
implemented, and remains as future work.
An interesting question is, to what extent should application users
be able to make annotations and operate similar tools in published
notebooks without coding and being exposed to the hackers's view?
Our prototype has not addressed this problem yet.

{\bf Content export} is not a capability we worked to support,
but R already has many packages for this. Our goal was to devise
ways of working where explicit export is less necessary.
However it is desirable to integrate results
through web protocols such as JSON. We did assume that RCloud
notebooks need to play well in the ecosystem of other tools,
and this worked out as intended, though we learned it also creates
a temptation to absorb features almost without limit. (Should
RCloud support templates for personal web pages and graphical
editing? Should it incorporate an email client and emacs?
Should it be able to push results to Facebook?)

{\bf Social-psychological incentives} and {\bf voting and ranking}
are supported through starring. This mechanism was employed often
by our test audience. An obvious next step would be to enhance
recommendations via relationships discovered by static and
dynamic code analysis. This should be done both within and across
collections of scripts (the latter being similar to Vistrails'
enhanced recommendations by clustering multiple workflows).
It should be valuable to hackers to know which packages are
frequently used together, or appear with a given record type
or data feed. In general, though, trivial or passive mechanisms
to collect data for recommendations are essential.

@@

{\bf Curation.} Even without more formal group management, users are
able to curate groups of related notebooks using the simple folder
system.  This is particularly effective for bringing together
training materials.

@@

{\bf Multiple language support.}
We did not anticipate having to back off so soon on the
assumption that programming is being done mainly in one
language (R). In retrospect, it should have been obvious
that many data science problems are already being solved
with cross-language approaches.

{\bf Versioning.}
A disadvantage is that some important aspects of the environment
are more difficult to manage in RCloud than in conventional systems.
Not only does it lack an explicit separation of the development and
deployment environments, but every version of every prototype is
shared by default. While this encourages collaboration on work
in progress, errors such as misconfiguration, mismatches between
versions of packages, and ordinary programming errors are also
easily shared and can affect production websites unintentionally.
This cannot be avoided entirely, but the power of sharing is worth
this price (as proven true with distributed systems in general).
Still, this problem needs more attention if the environment is
going to be scaled up to a wider number of users with fewer
informal channels to coordinate work. Effective sharing in RCloud
will require control over versioning.
Versioning must be managed in several places: in scripts, in the R environment
such as the installed R libraries and packages, and in the external
environment such as the operating system and even protocols spoken by
remote services. At one end of the scale, we have full control over the
versioning of scripts via git, though there is still a need for conventions
for example to name stable or working versions of scripts or versions known
to work together. The R environment is under the control of its package
manager. It is at least possible for RCloud to access information about
package versions and configurations, but support for checking compatibility
and maintaining multiple versions in the same environment is not strong.
At the other end of the scale, there is not much reason to expect version
control for the external environment. Most programmers rely on clean living
and a conservative approach to upgrades.

@@

{\bf Caching.}
An important consideration is how and where to introduce caching
in RCloud's distributed computation model. Caching can dramatically
improve performance in a way that is otherwise transparent to
application program semantics \cite{Callahan:2006:VVM, Guo:2010:TPI}.
Though caching is usually implicit, in some environments, such as
Vistrails, programmers may also have some explicit control over cache
management. This may be desirable to ensure the repeatability of
computations that rely on volatile or unreliable data sources.
For example, the stock ticker use case is one for which the data
might temporarily become unavailable, so caching could improve
reliability and consistency of results.  Alternatively, in a use case
involving text analysis through a topic modeling technique such as
Latent Dirichlet Allocation (LDA) that is relatively expensive,
we might want caching to improve performance. Currently we would
program this in RCloud by explicitly saving the analysis in a
persistent database, but it would be desirable to implement this
in a more general purpose associative cache. We envision cache
management being implemented in a new middle layer not in RCloud's
architecture today.

@@

Our back-end environment assumes a high degree of trust between users.
Access control for information security is delegated to the host
operating system and web server. In practice, most operating
systems and web servers rely either on coarse permission models,
which tend to be ineffective, or on detailed access control
lists, which tend to be cumbersome. 
Information security in RCloud should be re-examined, but more
sophisticated approaches such as information flow analysis are
still an active research area, and many problems have
been identified \cite{Moore:2011:SAF}. Having a richer
environment for collaboration and information sharing will encourage
practical applications for new approaches to information security
in visual analytics.

>>>>

Reconsidering Heer and Agrawala's design considerations, our
experience confirms the relevance of their proposals, and indicates
areas for further exploration. We briefly examine these aspects of
the visual analytics environment.

{\bf Shared artifacts and artifact histories} are key features
of RCloud. We observed that hackers readily used its capabilities
to share code and experiments, discuss data analysis, help one another
with programming problems, and to publish results by sharing URLs
instead of embedding screenshots in PowerPoint. Artifact histories are
maintained in git. We admit that git is not human-friendly, but many
hackers are familiar with it. Better graphical tools to explore and
control provenance would be an advantage.

{\bf Modularity and granularity.} The ability to segment work into
independent modules is a key to working in teams. It is a further
advantage if the units can be kept small, and team members can
realize benefits that are at least proportional to their work
on these units, which is referred to as granularity. RCloud's notebook
and versioning capabilities allow work to be divided into units as fine
as the underlying language allows, and versioning encourages making
incremental changes at low cost and without disrupting the work of others.

{\bf View sharing, bookmarking.} Most resources in RCloud are named
and accessed as URLs. This proved to be an effective mechanism for
sharing, and their ubiquity allows analyses to be integrated into
external processes and systems.

{\bf Discussion.} Annotation and commenting was another important goal.
Commenting is supported through github, but our hackers found it
awkward and did not exercise it as much as we expected.
More elaborate annotation was not implemented, and remains as future work.
An interesting question is, to what extent should application users
be able to make annotations in published notebooks without coding and
being exposed to the hackers's view?
The RCloud prototype has not addressed this problem yet.

{\bf Content export} is not a capability we worked to support,
but R already has many packages for this. Our goal was to devise
ways of working where explicit export is less necessary.
However it is desirable to integrate results
through web protocols such as JSON. We did assume that RCloud
notebooks need to play well in the ecosystem of other tools,
and this worked out as intended, though we learned it also creates
a temptation to absorb features almost without limit. (Should
RCloud support templates for personal web pages and graphical
editing? Should it incorporate an email client and emacs?
Should it be able to push content to Facebook?)

{\bf Social-psychological incentives} and {\bf voting and ranking}
are supported through starring. This mechanism was employed often
by our test audience. A potential next step would be to enhance
recommendations via relationships discovered by static and
dynamic code analysis. This could be done both within and across
collections of scripts (the latter being similar to Vistrails'
enhanced recommendations by clustering multiple workflows).
It should be highly valuable to hackers to know which packages
are frequently used together, or appear with a given record type
or data feed. Such knowledge is important, and difficult to acquire today.
In general, trivial or passive mechanisms to collect data for recommendations
are essential.

@@

{\bf Curation.} Even without more formal group management, users are
able to curate groups of related notebooks using the simple folder
system. This proved to be particularly effective for organizing
training materials.

@@

{\bf Multiple language support.}
We did not anticipate having to back off so soon on the
assumption that programming is done mainly in one language (R).
In retrospect, we should have realized that many data science problems
are already being solved with cross-language approaches.

{\bf Versioning.}
A disadvantage is that some important aspects of the environment
are more difficult to manage in RCloud than in conventional systems.
Not only does RCloud intentionally lack an explicit separation of the
development and deployment environments, but every version of every
prototype is shared by default. While this encourages collaboration on
work in progress, errors such as misconfiguration, mismatches between
versions of packages, and ordinary programming errors are also
easily shared and can affect production websites unintentionally.
This cannot be avoided entirely, but the power of sharing is worth
this price (as proven true with distributed systems in general).
Still, this problem needs more attention if the RCloud environment is
going to be scaled up to more users with fewer informal channels to
coordinate work.

Effective sharing in RCloud will require more control over versioning.
Versioning must be managed in several places: in scripts, in the R environment
such as the installed R libraries and packages, and in the external
environment such as the operating system and even protocols spoken by
remote services. At one end of the scale, we have full control over the
versioning of scripts via git, though there is still a need for conventions
for example to name stable or working versions of scripts or versions known
to work together. The R environment is under the control of its package
manager. It is at least possible for RCloud to access information about
package versions and configurations, but support for checking compatibility
and maintaining multiple versions in the same environment is not strong.
At the other end of the scale, there is not much reason to expect version
control for the external environment. Most programmers rely on clean living
and a conservative approach to global upgrades.

@@

{\bf Caching.}
An important consideration is how and where to introduce caching
in RCloud's distributed computation model. Caching can dramatically
improve performance in a way that is otherwise transparent to
application program semantics \cite{Callahan:2006:VVM, Guo:2010:TPI}.
Though caching is usually implicit, in some environments, such as
Vistrails, programmers may also have some explicit control over cache
management. This may be desirable to ensure the repeatability of
computations that rely on volatile or unreliable data sources.
For example, data fetched from a remote service (like historical stock data)
might temporarily become unavailable, so caching could improve
reliability and consistency of results. Alternatively, in a use case
involving text analysis through a topic modeling technique such as
Latent Dirichlet Allocation (LDA) that is relatively expensive,
we might want caching to improve performance. Currently we would
program this in RCloud by explicitly saving the analysis in a
persistent database, but it would be desirable to implement this
in a more general purpose associative cache. We envision cache
management being implemented in a new middle layer not in RCloud's
architecture today.

@@

Our back-end environment assumes a high degree of trust between users.
Access control for information security is delegated to the host
operating system and web server. In practice, most operating
systems and web servers rely either on coarse permission models,
which tend to be ineffective, or on detailed access control
lists, which tend to be cumbersome. 
Information security in RCloud should be re-examined, but more
sophisticated approaches such as information flow analysis are
still an active research area, and many unsolved problems have
been identified \cite{Moore:2011:SAF}. Having a richer environment for
collaboration and information sharing will encourage more research
and the adoption of better solutions to this problem.

### 2015-02-19 introduction.tex
Yes

Over fifty years ago, John Tukey published ``The Future of Data Analysis''
in which he defined a remarkably prescient agenda for the future of
data analysis and statistical computing. His vision has been realized
through environments like S and R, that started  a revolution by
integrating statistical graphics, computation, and robust techniques
for practical data modeling. Every day, many thousands of data scientists
and others specialists benefit from this brilliant vision.

@@

As a starting point, consider the role of a data science team within
a business or technical organization today.
Analysts work in loose or tight collaboration with colleagues and
domain experts.
Project teams vary in size, from just a few people to dozens or
more, even within one project's duration. Assignments are often
broad, and include tasks such as problem identification,
data wrangling, modeling, analysis, visualization, summarization
and interpretation of results, and explaining them and recommending
decisions, helping clients to realize the benefits of the analysis.
Eventually, knowledge or working prototypes created by data science teams
may be transferred to other organizations to employ them in production.
There are many details to these tasks. For example, data wrangling can involve
finding data, understanding its syntax and semantics, assessing data quality,
performing normalization and data quality remediation, and making the data
available to other tasks that will follow.

Visual analytics depends greatly on communication and collaboration.
At almost every step, detailed knowledge about data, code and tasks
is shared by collaborators. 
Further, data scientists are increasingly asked to work more closely
with business people who are domain specialists and less technically oriented.
Thus, data scientists and developers are being asked to become
very broad, and integrate work across the spectrum.

For example, interview comments found in {\it Data Scientists at Work}
by Sebastian Gutierrez illuminate the current practice of visual analytics.
There is a common theme, that data science or visual analytics is 
being done in teams that more share their work, both data and code,
more freely than before. We particularly want to point out the remarks
by Jonathan Lenaghan, who anticipates an environment for continuous
integration and publication of data analysis.

\begin{addmargin}[1em]{1em}  % left and right margin change
\small
\input{quotes}
\end{addmargin}

@@

This disjointed process inhibits the use of tools to bridge
the many gaps and to help people find resources.
For example, when code is shared, we still not may know where to find examples
that show how to use it. stephen{Why did I shift to first person?}
When we find a useful data source, we don't know what packages or
other data sources usually go along with it, or what problems with the data
others have already discovered and corrected, or where to obtain online feeds
to get updates of the data.

The current situation affects how well data science teams work. It limits
the ability to share work and to rapidly deploy and refine results.
We have seen this in our lab environment.
Other authors report similar findings.

Some symptoms of the current situation are:
\begin{itemize}
\item It is hard to find data, metadata, and previously hard-won knowledge about it.
\item Most coordination is done through meetings, whose content is not related to other artifacts and may not even be stored.
\item Production deployment requires porting code to a different environment or even completely rewriting it, thwarting continuous release.
\item Many tools adopt a standalone or single developer perspective,
not suited to collaboration and web deployment. 
\item Analysts find insufficient support for tracing events or issues from production back to the EDA process
\end{itemize}

In view of the opportunity to improve this situation,
we created a software environment that supports the end to end
visual analytics process for individuals and teams.
This environment knits together some familiar tools, and it
provides new features to find data and code; create experimental workbooks;
run experiments; annotate and deploy experiments as end-user websites or
as reusable, callable services; and to share, search and recommend these artifacts. The artifacts are stored in a version
control system that provides a common workspace, as well as needed control
and isolation between stable and experimental versions of code and other
resources.

Over the past two years, we prototyped this environment and deployed it
in a production community of data scientists, business analysts and other colleagues.
The platform today has over 200 active accounts, and several dozen people have forked
and customized code in the system.

@@

There is much previous work that inspired or influenced ours. Some
software prototypes that we learned from include:

{\bf Vistrails} as an important prototype of a scientific workflow
and provenance management system. The prototype helped the community
to understand the value of capturing aspects of the processes that
surround data analysis experiments and tools, including detailed
history, collaboration, and deployment.

{\bf iPython notebooks (Jupyter)} are the closest work we are aware of.
Of particular note,

{\bf RStudio, RShiny} and other packages based on R for creating and
publishing web content such as knitR, Rpubs, rCharts, and gg2v.

@@

{ManyEyes} is the best-known foundational work showing the potential for
integrating data visualization with social media.

Further afield, {\bf Electronic Lab Notebooks} are applications for organizing
data from lab experiments and sharing it within research teams \cite{Rubacha:ELN:2011}. In a sense, we hope to adapt and extend this concept to the work of
visual analytics teams.

@@

\item Technology transfer.
In most organizations, development of analyses and visualizations 
s done by \emph{hackers} and \emph{scripters} (using Kandel et al.'s
terminology~\cite{Kandel:2012:EDA}). \emph{Application users} 
gain the benefits of the tools developed by hackers and scripters.
Generally, the connection between these two worlds is made by IT staff,
who port or even rewrite code so it can run as a stable production service.
In an environment where business needs can change rapidly, this
process does not scale. Our objective is to connect the two worlds
of EDA and production.

\item Coexistence. In the current data science ecosystem, the
isolation of exploratory visualization and data analysis
environments hinders wider adoption of modern techniques.
The richness of interactive visualization tools is still somewhat
separated from the power of statistical programming environments.
There is an opportunity to provide a framework so that developments
on each side are more easily adopted by the other, and made available
in production services.

@@

\stephen{We could tell them what we're going to tell them here, but I'm
not sure that's good - unless we feel the reader will have trouble following
the path we are setting, it seems to disrupt the flow of the discussion.}

>>>>

Over fifty years ago, John Tukey published ``The Future of Data Analysis''
in which he defined a remarkably farsighted agenda for the future of
data analysis and statistical computing. His vision has been realized
through environments like S and R, that started a revolution by
integrating statistical graphics, computation, and robust techniques
for practical data modeling. Every day, many thousands of data scientists
and others specialists benefit from this astounding vision.

@@

As a starting point, consider the role of a data science team within
a business or technical organization today.
Analysts work in loose or tight collaboration with colleagues and
domain experts.
Project teams vary in size, from just a few people to dozens or
more, even within one project's duration. Assignments are often
broad, and include tasks such as problem identification,
data wrangling, modeling, analysis, visualization, summarization,
presentation and interpretation of results, and recommending
actions to help clients to realize the benefits of the analysis.
Eventually, knowledge or working prototypes created by data science teams
may be transferred to other organizations to employ them in production.
There are many details to these tasks. For example, data wrangling can involve
finding data, understanding its syntax and semantics, assessing data quality,
performing normalization and data quality remediation, and making the data
available to other tasks that will follow.

Visual analytics depends greatly on communication and collaboration.
At almost every step, detailed knowledge about data, code and tasks
is shared by collaborators. 
Further, data scientists are increasingly asked to work more closely
with business or domain specialists who may be less technically oriented.
Thus, data scientists and developers are being asked to become
very broad, and integrate work across the spectrum.

The following interview comments from
{\it Data Scientists at Work}
by Sebastian Gutierrez illuminate the current practice of teamwork
and sharing in visual analytics teams.
We particularly noted the remarks by
Jonathan Lenaghan, who anticipates an environment for continuous
integration and publication of data analysis.

\begin{addmargin}[1em]{1em}  % left and right margin change
\small
\stephen{Can we get away with \verb"\smaller"? Ha ha.}
\input{quotes}
\end{addmargin}

@@

This disjointed, inconsistent process inhibits the use of tools to bridge
the many gaps and to help people find resources.
For example, even when code is shared, we still not may know where to
find examples that show how to use it.
When we find a useful data source, we don't know what packages or
other data sources usually go along with it, what problems with the data
others have already discovered and corrected, or where to obtain online feeds
to get updates.

This situation definitely affects how well data science teams work.
It limits our ability to share work and to rapidly deploy and refine results.
We have seen this in our lab environment.
Other authors report similar findings.

Some symptoms of the current situation are:
\begin{itemize}
\item It is hard to find data, metadata, and knowledge about them.
\item Most coordination is done through meetings, whose content is not related to other artifacts and may not even be stored.
\item Production deployment requires porting code to a different environment or even completely rewriting it, thwarting continuous release.
\item Many tools adopt a standalone or single developer perspective,
not suited to collaboration and web deployment. 
\item Analysts find insufficient support for tracing events or issues from production back to the EDA process.
\end{itemize}

In view of the opportunity to improve this situation,
we created a software environment that supports the end to end
visual analytics process for individuals and teams.
This environment knits together some familiar tools, and 
provides new features to find data and code; create experimental workbooks;
run experiments; annotate and deploy experiments as end-user websites or
as reusable, callable services; and to share, search and recommend these artifacts. The artifacts are stored in a version
control system that provides a common workspace, as well as needed control
and isolation between stable and experimental versions of code and other
resources.

Over the past two years, we prototyped this environment and deployed it
in a production community of data scientists, business analysts and other colleagues.
The platform today has over 200 active accounts, and several dozen people have forked
and customized code in the system. Most of the active users are members of
the statistics research department of our lab, but some others are data
scientists and other collaborators in business units. \stephen{I hope this is right.}

@@

There is much previous work that inspired or influenced ours.
Indeed, many studies have addressed the requirements for future visual
analytics environments.
Previous work that we learned from includes:

{\bf Vistrails} as a landmark prototype of a scientific workflow
and provenance management system. This prototype helped the community
to understand the value of capturing aspects of the processes that
surround data analysis experiments and tools, including detailed
history, collaboration, and deployment.

{\bf iPython notebooks (Jupyter)} are the closest work we are aware of.
The goal of this project is to provide shared notebooks and a remote
execution environment for interpreted scripts. \stephen{Are there 
significant differences involving versioning, provenance, annotation
and other broad process support?}

{\bf RStudio, RShiny} and other packages based on R for creating and
publishing web content such as knitR, Rpubs, rCharts, and gg2v.
These tools are not collaborative, but they are aimed at better
graphics and web applications.

@@

{ManyEyes} is the best-known original work showing the potential for
integrating data visualization with social media.

Further afield, {\bf Electronic Lab Notebooks} are applications for organizing
and sharing data from scientitic lab experiments\cite{Rubacha:ELN:2011}.
In a sense, we hope to adapt and extend this concept to the work of
visual analytics teams.

@@

\item Technology transfer.
In most organizations, development of analyses and visualizations 
s done by \emph{hackers} and \emph{scripters} (adopting Kandel et al.'s
terminology~\cite{Kandel:2012:EDA}). \emph{Application users} 
gain the benefits of the tools developed by hackers and scripters.
Generally, the connection between these two worlds is made by IT staff,
who port or even rewrite code so it can run as a stable production service.
In an environment where business needs can change rapidly, this
process does not scale. Our objective is to merge the worlds
of EDA and production.

\item Coexistence. In the current data science ecosystem, the
isolation of exploratory visualization and data analysis
environments hinders wider adoption of modern techniques from each.
The richness of interactive visualization tools is still somewhat
separated from the power of statistical programming environments.
There is an opportunity to provide a framework so that developments
on each side are more easily adopted by the other, and made available
in production services.

@@

### 2015-02-19 quotes.tex
Yes

% part1.txt
Erin Shellman: Finally, prototyping our products so that internal
customers can use them early on has been crucial for
our success. It doesn't even have to be something
fancy. For instance, our recommendations preview
tool doesn't have a particularly interesting
visualization, but its enough to show the result of our
algorithms. Now we can shoot off a URL to internal
customers and it allows them to sit at their desk and
understand the behavior of our product and
experiment with it, and provide feedback way before
we're talking about getting it into production. This
has been super helpful and has been a really great
way to get people excited about what we're working
on. Building and maintaining those relationships are
just like anything else-- you always have to be
working on them. Nurturing those relationships are
part of the job, and if you leave them unattended,
they might not be there later.

@@

% part5.txt
Jonathan Lenaghan: First and foremost, it is very important
to be self-critical: always question your assumptions
and be paranoid about your outputs. That is the easy
part, In terms of skills that people should have if they
really want to succeed in the data science field, it is
essential to have good software engineering skills. So
even though we may hire people who come in with
very little programming experience, we work very
hard to instill in them very quickly the importance of
engineering, engineering practices, and a lot of good
agile programming practices, This is helpful to them
and us, as these can all be applied almost one-to-one
to data science right now.
If you look at dev ops right now, they have things
such as continuous integration, continuous build,
automated testing, and test harnesses-- a1l of which
map very well from the dev ops world to the data ops
(a phrase I stole from Red Monk) world very easily. I
think this is a very powerful notion. It is important to
have testing frameworks for all of your data, so that if
you make a code change, you can go back and test all
of your data. % Having an engineering mindset is

% part6.txt
Anna Smith: In addition to Bitly’s extraordinary data sets,
I was given all the resources that I needed. These were
resources that I’d only heard about but had never
seen. I went from asking what a Hadoop cluster was,
as my school didn't have one, to being able to work
with one. Now I could play with one to figure out how
to make my work better and how to change my
algorithms so they were cleaner and ran faster on
Hadoop. The whole transition was eye opening. Not
only that, I could also look at other people’s code and
play with their code and data sets as well. It was
fantastic and I was convinced that working with data
was my thing.

>>>>

% part1.txt
Erin Shellman [Nordstrom]: Finally, prototyping our products so that internal
customers can use them early on has been crucial for
our success. It doesn't even have to be something
fancy. For instance, our recommendations preview
tool doesn't have a particularly interesting
visualization, but its enough to show the result of our
algorithms. Now we can shoot off a URL to internal
customers and it allows them to sit at their desk and
understand the behavior of our product and
experiment with it, and provide feedback way before
we're talking about getting it into production. This
has been super helpful and has been a really great
way to get people excited about what we're working
on. Building and maintaining those relationships are
just like anything else-- you always have to be
working on them. Nurturing those relationships are
part of the job, and if you leave them unattended,
they might not be there later.

@@

% part5.txt
Jonathan Lenaghan [PlaceIQ]: First and foremost, it is very important
to be self-critical: always question your assumptions
and be paranoid about your outputs. That is the easy
part, In terms of skills that people should have if they
really want to succeed in the data science field, it is
essential to have good software engineering skills. So
even though we may hire people who come in with
very little programming experience, we work very
hard to instill in them very quickly the importance of
engineering, engineering practices, and a lot of good
agile programming practices, This is helpful to them
and us, as these can all be applied almost one-to-one
to data science right now.
If you look at dev ops right now, they have things
such as continuous integration, continuous build,
automated testing, and test harnesses-- a1l of which
map very well from the dev ops world to the data ops
(a phrase I stole from Red Monk) world very easily. I
think this is a very powerful notion. It is important to
have testing frameworks for all of your data, so that if
you make a code change, you can go back and test all
of your data. % Having an engineering mindset is

% part6.txt
Anna Smith: In addition to Bitly's extraordinary data sets,
I was given all the resources that I needed. These were
resources that I’d only heard about but had never
seen. I went from asking what a Hadoop cluster was,
as my school didn't have one, to being able to work
with one. Now I could play with one to figure out how
to make my work better and how to change my
algorithms so they were cleaner and ran faster on
Hadoop. The whole transition was eye opening. Not
only that, I could also look at other people’s code and
play with their code and data sets as well. It was
fantastic and I was convinced that working with data
was my thing.
